\Trill: Secure firewall-traversing networking

### 2012-11-12 6.858/proposal/proposal.tex
Delicious Italian food

\section*{Federated Identity}
% TODO

>>>>

\section*{Federated Identity}
As with other federated protocols like XMPP and email, \Trill identities will
be based on DNS.  Every domain name with a SRV record can act as a \Trill
identity realm, supporting email address-like identities (an \verb!addr-spec!
as defined in RFC 2822).

To grant a user an identity on a realm, the user first presents a username and
password to the server, after which the server delegates authority for that
name to the client by signing that client's key. This key-signing process is
the method by which peers can authenticate securely to each other without a
centralized broker.
